A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-21 main.tex
Paste a figure.

% 2つの設計手法と今回採用した理由

@@

@@

% Example of QCsp (mulmat)

>>>>

% 2つの設計手法と今回採用した理由
When we design type equivalence rules of \LMD, there are two design choices.
One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
Another is defining type equivalence directly by combination of type equivalence rules.
We adopt the latter one because it is convenient to handle CSP in the type equivalence.

@@

\begin{figure}
	\begin{center}
		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \andalso
		\infrule{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A}{\QApp} \\[2mm]
		\infrule{\G\V M \E N : \tau@{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau@A}{\QTB} \andalso
		\infrule{\G\V M \E N : \TW_\alpha \tau@A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau@{A\alpha}}{\QTBL} \\[2mm]
		\infrule{\G\V M\E N : \tau@A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau@A}{\QGen} \andalso
		\infrule{\G\V M \E N:\forall\alpha.\tau@A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp} \\[4mm]
		\infrule{\G\V M:\tau@A}{\G\V M\E M : \tau@A}{\QRefl} \andalso
		\infrule{\G\V M\E N : \tau@A}{\G\V N\E M : \tau@A}{\QSym} \andalso
		\infrule{\G\V M\E N : \tau@A \andalso \G\V N\E L : \tau@A}{\G\V M\E L : \tau@A}{\QTrans} \\[4mm]
		\infrule{\G,x:\sigma@A\V M:\tau@A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \andalso
		\infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
		\infrule{\G\V M \E N : \tau@A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \andalso
		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau@A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
		\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent} \andalso
		\caption{Tem Equivalence Rules}
		\label{fig:tem-equivalence-rules}
	\end{center}
\end{figure}

@@

% Example of QCsp (mulmat)
{
\newcommand{\I}{\textrm{Int}}
\newcommand{\M}{\textrm{Mat}}
\begin{align*}
	\text{mulmat}       & : \Pi x:\I.\Pi y:\I.(\TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha y) \to (\M\ \%_\alpha y\ \%_\alpha x) \to (\M\ z\ \%_\alpha x)) \\
	\text{mulmat}\ 3\ 5 & : \TW_\alpha \Pi z:\I.(\M\ z\ \%_\alpha 5) \to (\M\ \%_\alpha 5\ \%_\alpha 3) \to (\M\ z\ \%_\alpha 3)                     \\
	                    & (\E \TW_\alpha \Pi z:\I.(\M\ z\ 5) \to (\M\ 5\ 3) \to (\M\ z\ 3) )                                                         \\
\end{align*}
}
